---
title: "Homework5"
author: "Fifi"
date: "November 7, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE}
temperaturedata<-read.csv(file='Temperature change during a day.csv')
temperaturedata<-temperaturedata[-1,-1]
colnames(temperaturedata)<-c('Morning','Breakfast','Night')
temperaturedata$Morning<-as.character(temperaturedata$Morning)
temperaturedata$Morning<-as.numeric(temperaturedata$Morning)
temperaturedata$Breakfast<-as.character(temperaturedata$Breakfast)
temperaturedata$Breakfast<-as.numeric(temperaturedata$Breakfast)
temperaturedata$Night<-as.character(temperaturedata$Night)
temperaturedata$Night<-as.numeric(temperaturedata$Night)
```


###Does body temperature change significantly after eating?
###Paired t test between morning temperature and after breakfast termperature
```{r, echo=FALSE}
t.test(temperaturedata$Morning,temperaturedata$Breakfast,paired = TRUE)
```
p value>0.05, so there is no significant change of temperature after eating.

###Generate plot to see the difference
```{r, echo=FALSE}
hist(temperaturedata$Morning,breaks = 10,col=rgb(0,0,1,1/4), xlab = 'Temperature')
hist(temperaturedata$Breakfast,breaks = 10, col=rgb(1,0,1,1/4), xlab = 'Temperature', add = TRUE)
legend(36.0,6,c('Morning','After Breakfast'))
```

###Does body temperature change significantly after a full day of activity?
###Paired t test between morning temperature and night termperature
```{r, echo=FALSE}
t.test(temperaturedata$Morning,temperaturedata$Night,paired = TRUE)
```