---
title: "Homework5"
author: "Fifi"
date: "November 7, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
###Body Temperature Study

I am interested in knowing whether my body temperature changes significantly after eating and after a full day of acitivities, therefore I measured and collected my body temperature at 3 time points of the day: in the morning (immediately after waking), after breakfast, and at the night (right before go to bed).
I collected data for 23 days.

```{r, include=FALSE}
temperaturedata<-read.csv(file='Temperature change during a day.csv')
temperaturedata<-temperaturedata[-1,-1]
colnames(temperaturedata)<-c('Morning','Breakfast','Night')
temperaturedata$Morning<-as.character(temperaturedata$Morning)
temperaturedata$Morning<-as.numeric(temperaturedata$Morning)
temperaturedata$Breakfast<-as.character(temperaturedata$Breakfast)
temperaturedata$Breakfast<-as.numeric(temperaturedata$Breakfast)
temperaturedata$Night<-as.character(temperaturedata$Night)
temperaturedata$Night<-as.numeric(temperaturedata$Night)
```


###Paired t test between morning temperature and after breakfast termperature
Does body temperature change significantly after eating? A paired t test was done to calculate the significance of difference between 2 sets of temperature.
```{r, echo=FALSE}
t.test(temperaturedata$Morning,temperaturedata$Breakfast,paired = TRUE)
```
p value>0.05, so there is no significant change of temperature after eating.

###Generate plot to see the difference
```{r, echo=FALSE}
hist(temperaturedata$Morning,breaks = 10, main='Temperature at Morning and After Breakfast', col=rgb(0,0,1,1/4), xlab = 'Temperature')
hist(temperaturedata$Breakfast,breaks = 10, col=rgb(1,0,1,1/4), xlab = 'Temperature', add = TRUE)
legend('topright',c('Morning','After Breakfast'),fill  = c(rgb(0,0,1,1/4),rgb(1,0,1,1/4)))
```

Both distributions seem to be random between 35.2 and 36.2, which seems to be the range of my temperature. 

###Paired t test between morning temperature and night termperature
Does body temperature change significantly after a full day of activity?
```{r, echo=FALSE}
t.test(temperaturedata$Morning,temperaturedata$Night,paired = TRUE)
```
p value>0.05, so there is no significant change of temperature after a full day of activity.

###Generate plot to see the difference
```{r, echo=FALSE}
hist(temperaturedata$Morning,breaks = 10, main='Temperature at Morning and at Night', col=rgb(0,0,1,1/4), xlab = 'Temperature')
hist(temperaturedata$Night,breaks = 20, col=rgb(1,0,1,1/4), xlab = 'Temperature', add = TRUE)
legend('topright',c('Morning','Night'),fill  = c(rgb(0,0,1,1/4),rgb(1,0,1,1/4)))
```

Again the distributions seem to be random. 

